\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-06-24 src/algorithm.tex
latency

\begin{figure}[ht]
\centering
\input{fig-dp2}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sw$-path can be
efficiently computed by breaking the problem into the problem of embedding 
a $\sigma\alpha$-path into a $sv$-path (blue, dashed clouds) 
and the problem of embedding a $\beta\gamma$-path into $w$ (orange, dotted).
The $vw$-path must carry $b(\alpha\beta)$ bandwidth, 
The $\beta\gamma$-path is a minimum cost $\beta\gamma$-path 
that can be embedded into $w$.
}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\input{fig-dp2}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sw$-path can be
efficiently computed by breaking the problem into the problem of embedding 
a $\sigma\alpha$-path into a $sv$-path (blue, dashed rectangles) 
and the problem of embedding a $\beta\gamma$-path into $w$ (orange, dotted).
The $vw$-path must carry $b(\alpha\beta)$ bandwidth, 
The $\beta\gamma$-path is a minimum cost $\beta\gamma$-path 
that can be embedded into $w$.
}
\end{figure}

### 2017-06-24 src/latency.tex
latency

>>>>

We first describe an algorithm that, given a cost constraint $c$, 
finds an embedding that costs at most $c$ and has the minimum possible latency.
Once again, the algorithm maintains a pair of physical and virtual nodes,
$\gamma$ and $w$ respectively.
In each step it chooses a virtual edge $\alpha\beta$ and a physical node $v$
that are ascendant of $\gamma$ and $w$ respectively.
It then finds a $vw$-path that support the bandwidth of $\alpha\beta$ and
has the minimum possible latency with respect to this edge.
It also finds $\beta\gamma$-path that can be embedded into $w$ and has the 
minimum possible cost.
Finally it finds an embedding of a $\sigma\alpha$-path into a $sv$-path with 
the minimum possible latency recursively.
